---
title: "multireg package"
author: "Emma Wallentinson and Zaida Liendeborg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{multireg package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The multireg package calculates simple and multipel linear regression. The **linreg** function fits the regressen model using the ordinary least square method. Thereon, you get an object of class **linreg** containing the estimated beta coefficients with variance, residuals and their variance, fitted values, t-values, p-values and degrees of freedom. The residuals and the standardized residuals in the object of class **linreg** can also be plotted
against the fitted values. 

## The linreg function
Below is an example using the **linreg** function with the iris data set. 
```{r}
library(multireg)
linreg_object<-linreg(formula = Sepal.Width ~ Sepal.Length, data= iris)
names(linreg_object)
```

Different S3 methods were implemented in the **linreg** object and used to extract or plot results generated from the  **linreg** fucntion. These methods are as follows: 

```{r, eval=FALSE}
coef(linreg_object) # prints the coefficients
predict(linreg_object) # prints the fitted values
resid(linreg_object)# # prints the resiudals 
print(linreg_object) # prints the equation and the beta coefficients 
summary(linreg_object) # an output similar to the summary() statement of lm-objects. 
```

## The summary method

An example of the **summary()** function for class **linreg**: 

```{r, echo=FALSE, eval=FALSE}
summary(linreg_object)

```

## The plot method

An object of class **linreg** can be visualized in two different plots. The first one plots the residuals against the fitted values, and the second plots the square root of the absolute value of the standardized residuals aganst the fitted values. The way to do this is wih the **plot()** method: 

```{r, fig.width=7, fig.height=4}
library(ggplot2)
library(gridExtra)
plot(linreg_object)

```

## The coef method

**coef** takes an object of class **linreg** and prints out the beta coefficients estimates calculated by the regression model fitted by the **linreg** function. Example of application of **coef()**:

```{r, echo=FALSE}
coef(linreg_object)

```

## The resid method

**resid** method extracts the residuals of the fitted regression model by the **linreg**. Residuals are presented in a numeric vector. 

```{r, eval=FALSE}
resid(linreg_object)

```

## The predict method

The fitted values produced by the regression model can be extracted by using **predict()**. An example of the method application is shown below:

```{r, eval=FALSE}
predict(linreg_object)

```

## The print method

By using **print()**, the response variable and the explanatory variables used by the regression model prints out. It also gives the estimates of the beta coefficients. See example below: 

```{r, echo=FALSE}
print(linreg_object)

```
